### 2011-10-30 doc/theses/vitasek/chapter-2-research.tex
Thesis: in progress.

\chapter{Research}

@@

Fajt in \cite{fajt} introduces several algorithms to find XML keys (see \cite{keX}) in existing XML documents. Simple keys found this way can be translated to an equivalent ID attribute definition. This opens a new line of research: finding XML keys using an algorithm modified to look only for useful keys and then converting them to ID attributes.\\

>>>>

\chapter{Research}
\label{chapter-research}

@@

Fajt in \cite{fajt} introduces several algorithms to find XML keys (see \cite{keX}) in existing XML documents. Simple keys found this way can be translated to an equivalent ID attribute definition. The process is described in \cite[Ch.\ 9, s.\ 3]{vlist2002xml}. This opens a new line of research: finding XML keys using an algorithm modified to look only for \textit{useful} keys and then converting them to ID attributes.\\
